Exploring Bounds

### 2015-04-16 draft.tex
added plotkin.m, images there but broken

\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{verbatim}

%\usepackage{graphicx}
%\usepackage{caption}
%\usepackage{epstopdf}
%\usepackage{float}

@@

Before proving this bound, it is important to note that it is only valid when $d$ is sufficiently close to $n$.  For large $q$, this is can be a considerable limiting factor.
Consider that for $q=2$ our restriction is $n<2d$,  for $q=3$ our restriction is $n<\frac{3}{2}d$, for $q=4$ our restriction is $n<\frac{4}{3}d$, etc.

@@

Recall the Cauchy-Schwarz inequality, which states that 
\begin{equation}
\left(\sum_{i=1}^n x_i y_i \right )^2 \le \left(\sum_{i=1}^n x_i^2 \right ) \left(\sum_{i=1}^n y_i^2 \right )
\end{equation}

For our purposes, this means that 
\begin{equation}
\left(\sum_{\alpha\in\mathbb{F}_q} 1\cdot n_{i,\alpha} \right )^2 \le q \left(\sum_{\alpha\in\mathbb{F}_q} n_{i,\alpha}^2 \right )
\end{equation}

@@

\begin{equation} \label{plotkin_2}
S \le nM^2 - \sum_{i=1}^n q^{-1} \left(\sum_{\alpha\in\mathbb{F}_q} 1\cdot n_{i,\alpha} \right )^2 = nM^2 - \frac{nM^2}{q} = nrM^2
\end{equation}

Combining \ref{plotkin_1_5} and \ref{plotkin_2}, we get

\begin{equation}
M(M-1)d \le nrM^2
\end{equation}

which simplifies to

\begin{equation}
M \le \left\lfloor \frac{d}{d-rn} \right\rfloor
\end{equation}

@@

Applying the Sphere Packing bound, we have $A_2(7,4) = A_2(6,3) \le \frac{2^6}{1 + 6}$, 
giving us $A_2(7,4) \le 9$.

Applying the Plotkin bound, we have $A_2(7,4) \le \frac{4}{4-\frac{1}{2}\cdot7} = 8$.

@@

Applying Sphere Packing, we have  $A_2(9,6) = A_2(8,5) \le \frac{2^8}{1+8+28}$, giving us $A_2(n,d) \le 6$.

Applying the Plotkin bound, we have $A_2(9,6) \le \frac{6}{6-\frac{1}{2}\cdot9} = 4$.
\end{exmp}

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subfig}

%\usepackage{caption}
%\usepackage{epstopdf}
%\usepackage{float}

@@

Before proving this bound, it is important to note that it is only valid when $d$ is sufficiently close to $n$.  For large $q$, this is can be a considerable limiting factor.
Consider that our restriction is $n<2d$ for $q=2$, $n<\frac{3}{2}d$ for $q=3$, $n<\frac{4}{3}d$ for for $q=4$, etc.

@@

Recall the Cauchy-Schwarz inequality, which states that $\left(\sum_{i=1}^n x_i y_i \right )^2 \le \left(\sum_{i=1}^n x_i^2 \right ) \left(\sum_{i=1}^n y_i^2 \right )$
For our purposes, this means that $\left(\sum_{\alpha\in\mathbb{F}_q} 1\cdot n_{i,\alpha} \right )^2 \le q \left(\sum_{\alpha\in\mathbb{F}_q} n_{i,\alpha}^2 \right )$.

@@

\begin{equation} \label{plotkin_2}
S \le nM^2 - \sum_{i=1}^n q^{-1} \left(\sum_{\alpha\in\mathbb{F}_q} 1\cdot n_{i,\alpha} \right )^2 = nM^2 - \frac{nM^2}{q} = nrM^2.
\end{equation}

Combining \ref{plotkin_1_5} and \ref{plotkin_2}, we get $M(M-1)d \le nrM^2$, which simplifies to

\begin{equation}
M \le \left\lfloor \frac{d}{d-rn} \right\rfloor.
\end{equation}

@@

Applying the Sphere Packing bound, we have $A_2(7,4) = A_2(6,3) \le \frac{2^6}{1 + 6}$, 
giving us $A_2(7,4) \le \textbf{9}$.

Applying the Plotkin bound, we have $A_2(7,4) \le \frac{4}{4-\frac{1}{2}\cdot7} = \textbf{8}$.

@@

Applying Sphere Packing, we have  $A_2(9,6) = A_2(8,5) \le \frac{2^8}{1+8+28}$, giving us $A_2(n,d) \le \textbf{6}$.

Applying the Plotkin bound, we have $A_2(9,6) \le \frac{6}{6-\frac{1}{2}\cdot9} = \textbf{4}$.
\end{exmp}

It is also interesting to consider a more broader picture of what is going on here.  Below is a graph comparing rates of codes versus the Sphere Packing and Plotkin bounds
that we can calculate for those values for different values of q.

\begin{figure}
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{plotkin_q2.png}
  \caption{1a}
  \label{fig:sfig1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{plotkin_q3.png}
  \caption{1b}
  \label{fig:sfig2}
\end{subfigure}
\caption{plots of....}
\label{fig:fig}
\end{figure}
